---
title: "Covid Data Import and Graph"
author: "Patrick Cantwell"
date: "7/20/2020"
output: html_document
---

```{r packages, include=FALSE}
library("ggplot2")
library("readr")
library("readxl")
```

#Introduction
Hi! So as the README.md says, I don't really have any personal data to practice graphing with, so I decided to go with looking at some Covid data! Totally not stressful at all.


```{r}
column_names_tx <- c("date", "text", "skip", "skip", "numeric", "numeric", "skip", "numeric", "numeric")
texas_covid <- read_xlsx("us-counties covid 7-18-2020.xlsx", sheet = "texas_density_covid", col_types = column_names_tx)
texas_covid$county <- as.factor(texas_covid$county) #this coerces the "county" column to be made up of 21 factors
names(texas_covid)[names(texas_covid) == "cases/100,000"] <- "cases_per_ht" #this changes the name of the cases/100,000 column, as its previous name was causing difficulties
```

##Where did the data come from?
All of the data from this Excel sheet comes from several different sources:
*The population data comes from the U.S. Census' prediction of Texas counties, which can be found [here](https://www2.census.gov/programs-surveys/popest/tables/2010-2019/counties/totals/co-est2019-annres-48.xlsx)
*Texas county land areas (in square miles) was taken from the Wikipedia page [here](https://en.wikipedia.org/wiki/List_of_counties_in_Texas)
*Most importantly, the Covid-19 data comes from The New York Times' [GitHub page](https://github.com/nytimes/covid-19-data)

##Graphing

```{r}
ggplot(texas_covid, aes(date, cases_per_ht)) +
  geom_point()
```



