---
title: "HW03"
output: github_document
author: Laura Cespedes Arias
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
```

## Package loading
```{r load libraries}
library("ggplot2")
library("tidyverse")
library("lubridate")
```

## Data import and subsetting

I used a table with information about the coronavirus in the US, at the state level. This is available in a [NY Times repository](https://github.com/nytimes/covid-19-data).
```{r}
corona_by_state <- read.csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv",h=T)
```

Below, I made a few adjustments to the dataset. Specificically, I wanted the dates to be read as such, and created three separate columns with year, month and day. This WAS be important for making the figure.
```{r}
corona_by_state$date <- as.Date(corona_by_state$date)

corona_by_state = corona_by_state %>% 
  mutate(date = ymd(date)) %>% 
  mutate_at(vars(date), funs(year, month, day))

corona_by_state$month <- as.factor(corona_by_state$month)
```

Finally, I was only interested in the data for the states of Illinois and Arizona so I subseted the table:

```{r}
corona_ill_ari <- subset(corona_by_state,state=="Illinois"|state=="Arizona")
```

## Figure

I was interested in visualizing the number of cases per month and per state. So, this is what I did: 
```{r pressure, echo=TRUE}
ggplot(corona_ill_ari,mapping = aes(x = month, y = cases, fill=state, color=state)) +
  #To add boxes with a transparency
  geom_boxplot(alpha=0.6) +
  #To add points
  geom_jitter(position = position_jitterdodge(4)) +
  #To change the default grey background
  theme_bw()+
  #To add title and change the default size
  ggtitle(label="Coronavirus cases by month",subtitle="For Illinois and Arizona")+
  theme(plot.title = element_text(size = 20))+
  #To add axes labels
  xlab("Month (2020)") +
  ylab("Number of cases") +
  theme(axis.text.x = element_text(color="black", size=14, angle=45,hjust=1))+
  theme(axis.text.y = element_text(color="black", size=10))+
  theme(axis.title = element_text(color="black", size=20))+
  scale_x_discrete(labels=c("January","February","March","April","May","June","July"))+
  #To change the position of the legend and it's size
  theme(legend.position = c(0.25, 0.7))+
  theme(legend.title = element_text(size = 20),legend.text = element_text(size = 15))
```


