---
title: "HW03"
output: github_document
author: Laura Cespedes Arias
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
```

## Package loading
```{r load libraries}
library("ggplot2")
library("readr")
```

## Data import and subsetting

I used data from a project I am working on at the moment. The table I upload here is incomplete, because the results of the projects are not published yet (we are in the process!). Here I imported data of above ground forest biomass, which is a measure of "forest cover". The data table was produced by using coordinates of count stations (for birds) that we visited and then using a raster layer from [Baccini et al 2017](https://science.sciencemag.org/content/early/2017/09/27/science.aam5962?versioned=true) to extract the above ground forest biomass for each of the coordinates. I extracted these values using the raster layer at two different resolutions (30 meters and 1 km) In the data table there is also a categorical variable for habitat type
```{r}
biomass_URL <- "https://raw.githubusercontent.com/lcespedesarias/HW03/master/Arremon/Physical_condition.csv"
biomass <- read.csv(url(arremon_URL),h=T,sep=";")
```

Below, I made a few adjustments to the dataset. Specificically, I wanted the dates to be read as such, and created three separate columns with year, month and day. This WAS be important for making the figure.
```{r}
```


## Figure

I was interested in visualizing the number of cases per month and per state. So, this is what I did: 
```{r pressure, echo=TRUE}
ggplot(corona_ill_ari,mapping = aes(x = month, y = cases, fill=state, color=state)) +
  #To add boxes with a transparency
  geom_boxplot(alpha=0.6) +
  #To add points
  geom_jitter(position = position_jitterdodge(4)) +
  #To change the default grey background
  theme_bw()+
  #To add title and change the default size
  ggtitle(label="Coronavirus cases by month",subtitle="For Illinois and Arizona")+
  theme(plot.title = element_text(size = 20))+
  #To add axes labels
  xlab("Month (2020)") +
  ylab("Number of cases") +
  theme(axis.text.x = element_text(color="black", size=14, angle=45,hjust=1))+
  theme(axis.text.y = element_text(color="black", size=10))+
  theme(axis.title = element_text(color="black", size=20))+
  scale_x_discrete(labels=c("January","February","March","April","May","June","July"))+
  #To change the position of the legend and it's size
  theme(legend.position = c(0.25, 0.7))+
  theme(legend.title = element_text(size = 20),legend.text = element_text(size = 15))
```


