---
title: "HW03_Xiaoshan"
output: github_document
author: Xiaoshan Ke
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("ggplot2")
library("forcats")
library("dplyr")

```
I am curious about how did the data change for the five states where covid-19 cases were first confirmed, so I will select them from the large dataset and am going to make a plot them.

## Importing data
For states that have confirmed cases earlier, they will appear more frequent in the table than others. Therefore I will find them by counting the frequency of each states. To do this, I used the fct_infreq() from the existed r library "forcats". 

```{r}
states <- read.csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv"))
states$state = fct_infreq(states$state)
head(summary(states$state),5)
```

## Making the plot
Since the five states are Washington, Illinois, California, Arizona, and Massachusetts, I will select them individually and combining them into a large dataset, then make a plot. I think this might be a little bit complicated and I am wondering if there's a simpler way of doing this.


```{r}
five <- states %>%
  filter(state == "California"|state == "Illinois"|state == "Washington"|state == "Arizona"|state == "Massachusetts")

ggplot(five, aes(date, cases, group = state)) +
  geom_line(aes(color = state)) +
  scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+  
  ggtitle("COVID-19 data for the first five states that had confirmed cases")
```



