---
title: "HW03_Julia"
author: "Julia Shangguan"
date: "7/19/2020"
output: github_document 
---

```{r setup, include = TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HWO3: Looking at COVID-related data

There is a lot of cool data available from the Pew Research Center. Here is where I downloaded my dataset from: [PewResearchCenter](https://www.journalism.org/dataset/covid-19-late-april-2020/)

**Loading in necessary packages and installing packages:**
```{r load libraries}
install.packages('survey') #install this package for analysis of data analysis
library(survey)
install.packages('tidyverse')
library(tidyverse)
library("ggplot2")
library(foreign) #needed to import my dataset
library(scales) #needed to later convert my x-axis labels from decimal to percent
```

**Importing my dataset as an R data.frame:**
```{r}
Covid_data <- read.spss("Pathways April 2020 (ATP W66).sav", to.data.frame = TRUE) 
```

**The survey question I will be examining is**: "All in all, do you think that the coronavirus outbreak has been…"

* made a bigger deal than it really is

* made a smaller deal than it really is

* approached about right

* no answer


A lot of my time was spent trying to understand how this dataset was organized. I found this [document](https://www.pewresearch.org/wp-content/uploads/2018/05/Codebook-and-instructions-for-working-with-ATP-data.pdf) that explained what the demographic profile variables meant. The variables corresponding to each survey question response were included in this document titled [Pathways April 2020 ATP W66](Pathways_April 2020_ATPW66_ Topline.pdf) which comes with the dataset download. I am interested in responses as stratified by age (F_AGECAT) and self-reported political party (F_PARTY_FINAL).

```{r}
#names(Covid_data) #variables corresponding to each survey question
```

I will be plotting weighted survey estimates based on the variable WEIGHT_W66 because "data for all Pew Research Center reports are analyzed using this weight."

First, I am cleaning up my dataframe and limiting the dataset to only the columns I need. 
```{r}
#limit to select columns, also renaming some columns
select_Covid_data <- Covid_data %>%
  select(weight = WEIGHT_W66, response = COVIDDEAL_W66, Age = F_AGECAT, Party = F_PARTY_FINAL) 

head(select_Covid_data) #checking that it worked
```

I am rearranging the data so that I can easily calculate weighted summary stats by each demographic group by reshaping data to a "long" format. I'm not sure how to describe this, but [this article](https://medium.com/pew-research-center-decoded/using-tidyverse-tools-with-pew-research-center-survey-data-in-r-bdfe61de0909) touches upon it; this article was also just super helpful in general for formatting Pew Research data sets. 
```{r}
select_Covid_data_long <- select_Covid_data %>%
  gather(key = subgroup_variable, value = subgroup, Age, Party)
```

I can now get the weighted summaries for the subgroup variables by adding a third grouping variable. 

```{r}

newstrust <-  select_Covid_data_long %>%
  group_by(subgroup_variable, subgroup, response) %>% 
  summarise(weighted_n = sum(weight))  %>%  #get the total sums of weights n for each category 
  group_by(subgroup) %>% #group to get subgroup category size
#add columns to get proportion values
  mutate(weighted_group_size = sum(weighted_n), 
         weighted_percent_responders = weighted_n / weighted_group_size
         )
```

OK, I have spent a lot of time trying to figure out how to manipulate this data set instead of graphing it...which was not supposed to be the focus of this assignment...I didn't realize choosing this type of data set was going to be this much work. Now I can finally graph it and try to make it visually informative.

```{r}
#renaming the "response" subvariables
newstrust$response <- 
 recode( newstrust$response, "Made a BIGGER deal than it really is" = "Made a \nbigger deal than \nit really is", "Made a SMALLER deal than it really is" = "Made a \nsmaller deal than \nit really is", "Approached about right" = "Approached \nabout right", "Refused" = "No answer")

ggplot(newstrust, aes(x = weighted_percent_responders, y = subgroup, fill = factor(subgroup))) +
   geom_bar(stat='identity') +
   scale_x_continuous(name = "Weighted percent of responses", labels = percent) +
   scale_y_discrete(name = "Subgroup") +
         facet_grid(cols = vars(response),
                    rows = vars(subgroup_variable),
                    scales = "free_y",
                    space = "free") +
         theme(axis.title.y = element_blank()) +
         theme_linedraw() +
  labs(title = "American Opinion about Covid19 News Coverage", 
       subtitle = "Survey Question: 'All in all, do you think that the \ncoronavirus outbreak has been...'", 
       caption = "*Where 'refused' represents 'refused to answer'" ) +
   theme(plot.title = element_text(hjust = 0.5), 
         plot.subtitle = element_text(hjust = 0.5), 
         axis.text.x = element_text(angle = 45, vjust = 0.5), 
         legend.position = "None") 

```