---
title: "HW3"
author: "Angela Chun"
date: "7/19/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries, include=FALSE}
library("ggplot2")
library("tidyverse")
library("lubridate")
library("readxl")
library(dplyr)
library(tidyr)
```

# The Data

This is a small portion of a data I made last year for my research on generating allergic airway inflammation mice models.
We examined cellular phenotypes in the mice models of allergic asthma sensitized with different adjuvants.
The aim of our study was to determine immunologic cellular characteristics in mouse asthma models induced by ovalbumin (OVA) and a variety of adjuvants. 

The data shows the percentages of CD+ Th cells showing 4 different cytokines within lung, according to the adjuvants the mice were sensitized with.

The adjuvants I used were:

1. Ovalbumin (OVA)
2. Lipopolysaccharide (LPS)
3. Alhydrogel (Alum)
4. Papain

The cytoines of interests were:

1. IL-4
2. IL-5
3. IFN-γ
4. IL-17A

Three mice (indicated by the numbers 1, 2, and 3) were used per adjuvant to generate a total of 12 mice models.

# Exporting the excel file
I used read_excel() from the "readxl" package.

```{r export}
Tsti_Data <- read_excel("Tsti Data.xlsx", sheet = 1)
Tsti_Data

```


# The Graph

I wanted  to display four separate graphs according to the cytokines the T cells were expressing

- Used facet_wrap() to achieve this.

I also wanted to group the mice models according to the adjuvants groups 
- Decided to do this by color/fill.



```{r graph}
Tsti_Data %>%
  gather(Tsti_Data, value, -Adjuvant) %>%
  ggplot(aes(Adjuvant, value, fill = Adjuvant)) + 
  geom_bar(stat = "identity") + 
  
  #Manually changed the colors so each adjuvant group would display the same color
  
  scale_fill_manual(values = c("darkturquoise", "darkturquoise", "darkturquoise", "brown1", "brown1", "brown1", "springgreen4", "springgreen4", "springgreen4", "orange", "orange", "orange")) + 
  facet_wrap(~Tsti_Data) +
  
  #Changed the title and axis labels
  
  labs(title = "Percentage of intracellular cytokines among lung CD4+ Th cells of mice \nsensitized with different adjuvants", x = "Sensitization (Adjuvant)", y = "% in CD4+ T cells", subtitle = "Following PMA/ionomycin stimulation, CD4+ Th cells in lungs of mice sensitized \nwith different adjuvants were analyzed to evaluate their intracellular cytokine levels") + 
  theme_bw() + 
  
  #The x axis text were overlapping, so fixed it by adjusting the angle and height and also applied the color scheme.
  
  theme(axis.text.x = element_text(angle = 45, vjust = 0.7, color = c("darkturquoise", "darkturquoise", "darkturquoise", "brown1", "brown1", "brown1", "springgreen4", "springgreen4", "springgreen4", "orange", "orange", "orange"))) 

```