---
title: "HW3_CovidData"
author: "Olubusayo Bolonduro"
date: "7/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
Both the first coronavirus case in the US and the first coronavirus-related death were confirmed in Washington State. The first case was confirmed on January 21st, while  Seattle and King County confirmed the first death on February 29th. Given that I was born and raised in the King County Seattle area, these reports truly did hit too close to home. 

For this assignment I wanted to observe county-level, state-level, and U.S. National-level trends for confirmed COVID-19 cases using COVID-19 data from King County and Washington State. 


```{r message = FALSE}
library(ggplot2)
library(dplyr)
```


## Importing COVID-19 data 

```{r}
counties <- read.csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv"))
states <- read.csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv"))
us <- read.csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us.csv"))

king_county <- counties %>%
  filter(county == "King")
washington_state <- states%>%
  filter(state == "Washington")
```

## Plotting Data



```{r}
## individual plots for Cases

king_county$date <- as.Date(king_county$date)
#2,252,782 King County residents according to 2019 census data
kingcounty_plot <- ggplot(king_county, aes(date, cases/2252782 * 100)) +
  geom_point()+
  labs(x="Month", y = "Percent of Population with Confirmed Cases", title = "King County Confirmed Cases")+
  theme(plot.title = element_text(hjust = 0.5))
  #scale_x_date(date_labels = "%b")
#kingcounty_plot

washington_state$date <- as.Date(washington_state$date)
#7,614,893 Washington state residents accoding to 2019 census data
washingtonstate_plot <-ggplot(washington_state, aes(date, cases/7614893 * 100)) +
  geom_point()+
  labs(x="Month", y = "Percent of Population with Confirmed Cases", title = "Washington State Confirmed Cases")+
  theme(plot.title = element_text(hjust = 0.5))
  #scale_x_date(date_labels = "%b")
#washingtonstate_plot

us$date <-as.Date(us$date)  
#328,239,523 US residents according to 2019 census data
us_plot<- ggplot(us, aes(date, cases/328239523 * 100)) +
  geom_point()+
  labs(x="Month", y = "Percent of Population with Confirmed Cases", title = "United States Confirmed Cases")+
  theme(plot.title = element_text(hjust = 0.5))
  #scale_x_date(date_labels = "%b")
#us_plot
    

##overlayed plot for Cases 

ggplot()+
  geom_line(data = king_county, aes(x = date,y = cases/2252782 * 100, color = 'green')) +
  geom_line(data = washington_state, aes(x = date, y = cases/7614893 * 100, color = 'blue'))+
  geom_line(data = us, aes(x = date, y = cases/328239523 * 100, color  = 'red'))+
  labs(x="Month", y = "Percent of Population with Confirmed Cases", color = "data", title = "Confirmed Cases")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_x_date(date_labels = "%b")+
  scale_color_discrete(name ="Key", labels = c("King County","Washington State","United States"))

```

